Certified Knowledge Compilation \\ with Application to Formally Verified Model Counting

### 2024-01-07 doc/JAIR/lean-section.tex
Minor typo

We set out to formally verify the system with two goals in mind:
first, to ensure that the CPOG framework is mathematically sound;
and second, to implement correct-by-construction proof checking
and ring evaluation (the ``Trusted Code'' components of \ref{fig:chain}).
These two goals are achieved with a single proof development
in the \lean{} programming language~\cite{demoura:cade:2021}.
Verification was greatly aided
by the Aesop~\cite{23limperg_aesop_white_box_best_first_proof_search_lean}
automated proof search tactic.
\lean{} is based on a logical foundation
in which expressions have a computational interpretation.
As in other proof assistants such as Isabelle and Coq,
functions defined in the formal system
can be compiled to machine code.
At the same time,
we can state and prove claims about them within the same system,
thereby verifying that our functions compute the intended results.
In this section,
we describe the functionality we implemented,
what we proved about it,
and the assumptions we made.

>>>>

We set out to formally verify the system with two goals in mind:
first, to ensure that the CPOG framework is mathematically sound;
and second, to implement correct-by-construction proof checking
and ring evaluation (the ``Trusted Code'' components of Figure~\ref{fig:chain}).
These two goals are achieved with a single proof development
in the \lean{} programming language~\cite{demoura:cade:2021}.
Verification was greatly aided
by the Aesop~\cite{23limperg_aesop_white_box_best_first_proof_search_lean}
automated proof search tactic.
\lean{} is based on a logical foundation
in which expressions have a computational interpretation.
As in other proof assistants such as Isabelle and Coq,
functions defined in the formal system
can be compiled to machine code.
At the same time,
we can state and prove claims about them within the same system,
thereby verifying that our functions compute the intended results.
In this section,
we describe the functionality we implemented,
what we proved about it,
and the assumptions we made.
